Setup for flash project

### 2018-02-11 analysis/CVtemplate.Rmd
Files commited by wflow_commit.

---
title: "template for CV in RCC"
author: "Wei"
date: 10-03
output: html_document
---

@@

# methods
flashG_wrapper = function(Y, missindex, rank_max,type = "constant"){
  # delete the value in the missing position
  Y_miss = Y
  Y_miss[missindex$rowindex, missindex$colindex] = NA
  data = flashr2::flash_set_data(Y_miss)
  g_flash = flashr2::flash_add_greedy(data,Kmax=rank_max,ash_param=list(method = "fdr"),var_type = type)
  misshat_flash = g_flash$EL %*% t(g_flash$EF)
  rmse = sqrt(mean((Y[missindex$rowindex, missindex$colindex] - misshat_flash[missindex$rowindex, missindex$colindex])^2))
  return(rmse)
}

flashB_wrapper = function(Y, missindex, rank_max,type = "constant"){
  # delete the value in the missing position
  Y_miss = Y
  Y_miss[missindex$rowindex, missindex$colindex] = NA
  data = flashr2::flash_set_data(Y_miss)
  g_flash = flashr2::flash_add_greedy(data,Kmax=rank_max,ash_param=list(method = "fdr"),var_type = type)
  b_flash = flash_backfit(data,g_flash)
  misshat_flash = b_flash$EL %*% t(b_flash$EF)
  rmse = sqrt(mean((Y[missindex$rowindex, missindex$colindex] - misshat_flash[missindex$rowindex, missindex$colindex])^2))
  return(rmse)
}

@@

```{r}
library(R.matlab)
# call the R functions
source("~/HG/flash/data/CVmissflashr2/template/Rfunction.R")
# read the data
# you need to change the path for different data
Y_data = R.matlab::readMat("~/HG/flash/data/CVmissflashr2/Breastcancer/example.mat")
Y = Y_data$Y
N = dim(Y)[1]
P = dim(Y)[2]
Y = Y - rowMeans(Y) %*% t(rep(1,P))
result = c()
missindex = miss_gen(Y, percent = 0.1)
# creat a folder for the output and matlab in the folder we make
if(file.exists("NBSFAout")){
  unlink("NBSFAout", recursive= T)
}
system("mkdir NBSFAout")
# write the missing index
writeMat("./NBSFAout/missindex.mat", missindex = missindex)

flashG_rmse = flashG_wrapper(Y, missindex, rank_max = 50)
pmd_rmse  = PMD_wrapper(Y, missindex, rank_max= 50 )
soft_rmse = softImpute_wrapper(Y, missindex, rank_max = 50)
# then call the matlab estiamtion 
# this for the folder of the data
system("matlab -nosplash -nodesktop -r \"addpath(\'~/HG/flash/data/CVmissflashr2/template\'); run(\'missvalue.m\');exit;\" ")
g_nsfa = readMat("./NBSFAout/NSFAresult.mat")
nsfa_rmse = as.vector(g_nsfa$rmse.NSFA)

@@

#SBATCH --job-name=arrayJob
#SBATCH --output=/home/weidong/HG/flash/data/CVmissflashr2/Breastcancer/outlog/arrayJob_%A_%a.out
#SBATCH --error=/home/weidong/HG/flash/data/CVmissflashr2/Breastcancer/outlog/arrayJob_%A_%a.err
#SBATCH --array=1-100
#SBATCH --time=06:00:00
#SBATCH --partition=broadwl
#SBATCH --ntasks=1
#SBATCH --mem-per-cpu=6000

@@

# Print this sub-job's task ID
cd /home/weidong/HG/flash/data/CVmissflashr2/Breastcancer
mkdir test${SLURM_ARRAY_TASK_ID}
cd test${SLURM_ARRAY_TASK_ID}
Rscript --verbose /home/weidong/HG/flash/data/CVmissflashr2/Breastcancer/runR.R
```

>>>>

---
title: "template for CV in RCC"
author: "Wei"
output: 
  html_document:
    code_folding: hide
---

@@

# methods
flashG_wrapper = function(Y, missindex, rank_max,type = "constant"){
  # delete the value in the missing position
  Y_miss = Y
  Y_miss[missindex$rowindex, missindex$colindex] = NA
  data = flashr::flash_set_data(Y_miss)
  g_flash = flashr::flash_add_greedy(data,Kmax=rank_max,ash_param=list(method = "fdr"),var_type = type)
  misshat_flash = g_flash$EL %*% t(g_flash$EF)
  rmse = sqrt(mean((Y[missindex$rowindex, missindex$colindex] - misshat_flash[missindex$rowindex, missindex$colindex])^2))
  return(rmse)
}

flashB_wrapper = function(Y, missindex, rank_max,type = "constant"){
  # delete the value in the missing position
  Y_miss = Y
  Y_miss[missindex$rowindex, missindex$colindex] = NA
  data = flashr::flash_set_data(Y_miss)
  g_flash = flashr::flash_add_greedy(data,Kmax=rank_max,ash_param=list(method = "fdr"),var_type = type)
  b_flash = flash_backfit(data,g_flash)
  misshat_flash = b_flash$EL %*% t(b_flash$EF)
  rmse = sqrt(mean((Y[missindex$rowindex, missindex$colindex] - misshat_flash[missindex$rowindex, missindex$colindex])^2))
  return(rmse)
}

@@

```
library(R.matlab)
# call the R functions
source("~/HG/flash/data/CVmissflashr/template/Rfunction.R")
# read the data
# you need to change the path for different data
Y_data = R.matlab::readMat("~/HG/flash/data/CVmissflashr/Breastcancer/example.mat")
Y = Y_data$Y
N = dim(Y)[1]
P = dim(Y)[2]
Y = Y - rowMeans(Y) %*% t(rep(1,P))
result = c()
missindex = miss_gen(Y, percent = 0.1)
# creat a folder for the output and matlab in the folder we make
if(file.exists("NBSFAout")){
  unlink("NBSFAout", recursive= T)
}
system("mkdir NBSFAout")
# write the missing index
writeMat("./NBSFAout/missindex.mat", missindex = missindex)

flashG_rmse = flashG_wrapper(Y, missindex, rank_max = 50)
pmd_rmse  = PMD_wrapper(Y, missindex, rank_max= 50 )
soft_rmse = softImpute_wrapper(Y, missindex, rank_max = 50)
# then call the matlab estiamtion 
# this for the folder of the data
system("matlab -nosplash -nodesktop -r \"addpath(\'~/HG/flash/data/CVmissflashr/template\'); run(\'missvalue.m\');exit;\" ")
g_nsfa = readMat("./NBSFAout/NSFAresult.mat")
nsfa_rmse = as.vector(g_nsfa$rmse.NSFA)

@@

#SBATCH --job-name=arrayJob
#SBATCH --output=/home/weidong/HG/flash/data/CVmissflashr/Breastcancer/outlog/arrayJob_%A_%a.out
#SBATCH --error=/home/weidong/HG/flash/data/CVmissflashr/Breastcancer/outlog/arrayJob_%A_%a.err
#SBATCH --array=1-100
#SBATCH --time=06:00:00
#SBATCH --partition=broadwl
#SBATCH --ntasks=1
#SBATCH --mem-per-cpu=6000

@@

# Print this sub-job's task ID
cd /home/weidong/HG/flash/data/CVmissflashr/Breastcancer
mkdir test${SLURM_ARRAY_TASK_ID}
cd test${SLURM_ARRAY_TASK_ID}
Rscript --verbose /home/weidong/HG/flash/data/CVmissflashr/Breastcancer/runR.R
```

### 2018-02-11 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

---
title: "Template for GTEx example on cluster"
author: "wei"
date: 09-29
output: 
  html_document:
    code_folding: hide
---

@@

1 please git clone the `flashr2` on PPS.

`git clone https://github.com/stephenslab/flashr2.git`

2 install `flashr2` locally

`R CMD build flashr2`

`R CMD INSTALL flashr2_0.2-2.tar.gz`

@@

```
mkdir testflashr2
cd testflashr2
cp gtexEQTL_zscore.rds GTEX/testflashr2/
```

@@

```
library(ashr)
library(flashr2)
load("./gtexEQTL_zscore.rds")
Y = t(zscore)
data = flash_set_data(Y)
f_greedy = flash_add_greedy(data,Kmax=60)
f_greedy_bf = flash_backfit(data,f_greedy)
#f_greedy = flash_add_greedy(data,Kmax=60,var_type = "by_column",ash_param=list(method = "fdr"))
#f_greedy_bf = flash_backfit(data,f_greedy,var_type = "by_column",ash_param=list(method = "fdr"))
saveRDS(f_greedy,file = "./output/gflashvarcol.rds")
saveRDS(f_greedy_bf,file = "./output/bflashvarcol.rds")
```

@@

#SBATCH --job-name=arrayJob
#SBATCH --output=/home/weidong/HG/flash/data/GTEX/testflashr2/outlog/arrayJob_%A_%a.out
#SBATCH --error=/home/weidong/HG/flash/data/GTEX/testflashr2/outlog/arrayJob_%A_%a.err
#SBATCH --array=1
#SBATCH --time=30:00:00
#SBATCH --partition=mstephens
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --mem-per-cpu=8G

@@

# Print this sub-job's task ID
cd /home/weidong/HG/flash/data/GTEX/testflashr2
Rscript --verbose flashwrapper.R
```

you can substitute the folder path `/home/weidong/HG/flash/data/GTEX/testflashr2`. and we call this `.sbatch` file as `runflash.sbatch`

@@

@@

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=9), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "factor values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.8, keywidth = 0.3))
  #ggsave("flashr2GTEx1.pdf", width = 8, height = 11)

@@

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=9), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "factor values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.8, keywidth = 0.3))
  #ggsave("flashr2GTEx2.pdf", width = 8, height = 10)
```

the plots are

<img src="figure/flashr2GTEx1.pdf" alt="the plot is in analysis/flashr2GTEx1.pdf"  width="4200" height="4200">

<img src="figure/flashr2GTEx2.pdf" alt="the plot is in analysis/flashr2GTEx1.pdf"  width="4200" height="4200">

## an example to run SFA on RCC or PPS

>>>>

---
title: "Template for GTEx example on cluster"
author: "wei"
output: 
  html_document:
    code_folding: hide
---

@@

1 please git clone the `flashr` on PPS.

`git clone https://github.com/stephenslab/flashr.git`

2 install `flashr` locally

`R CMD build flashr`

`R CMD INSTALL flashr_0.2-2.tar.gz`

@@

```
mkdir testflashr
cd testflashr
cp gtexEQTL_zscore.rds GTEX/testflashr/
```

@@

```
library(ashr)
library(flashr)
load("./gtexEQTL_zscore.rds")
Y = t(zscore)
data = flash_set_data(Y)
f_greedy = flash_add_greedy(data,Kmax=60)
f_greedy_bf = flash_backfit(data,f_greedy)
#f_greedy = flash_add_greedy(data,Kmax=60,var_type = "by_column",ash_param=list(method = "fdr"))
#f_greedy_bf = flash_backfit(data,f_greedy,var_type = "by_column",ash_param=list(method = "fdr"))
saveRDS(f_greedy,file = "./output/gflashvarcol.rds")
saveRDS(f_greedy_bf,file = "./output/bflashvarcol.rds")
```

@@

#SBATCH --job-name=arrayJob
#SBATCH --output=/home/weidong/HG/flash/data/GTEX/testflashr/outlog/arrayJob_%A_%a.out
#SBATCH --error=/home/weidong/HG/flash/data/GTEX/testflashr/outlog/arrayJob_%A_%a.err
#SBATCH --array=1
#SBATCH --time=30:00:00
#SBATCH --partition=mstephens
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --mem-per-cpu=8G

@@

# Print this sub-job's task ID
cd /home/weidong/HG/flash/data/GTEX/testflashr
Rscript --verbose flashwrapper.R
```

you can substitute the folder path `/home/weidong/HG/flash/data/GTEX/testflashr`. and we call this `.sbatch` file as `runflash.sbatch`

@@

Get the result from `flashr` as `bflashvarcol.rds` (backfitting result).

@@

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=9), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "factor values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.8, keywidth = 0.3))
  #ggsave("flashrGTEx1.pdf", width = 8, height = 11)

@@

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=9), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "factor values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.8, keywidth = 0.3))
  #ggsave("flashrGTEx2.pdf", width = 8, height = 10)
```

## An example to run SFA on RCC or PPS

### 2018-02-11 analysis/MSErank1sim.Rmd
Files commited by wflow_commit.

---
title: "MSE for rank_1 simulation"
author: "wei wang"
date: 17-12-09
output: 
  html_document:
    code_folding: hide
---

@@

PN.wrapper = function(Y_data){
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  library(ebnm)
  library(flashr2)
  data =  flashr2::flash_set_data(Y)
  g_flash = flashr2::flash_r1(data,verbose=F,var_type = "constant",ebnm_fn = ebnm_pn)
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}

flash.wrapper = function(Y_data){
  # missindex is a matirx with 3 column here: i j x
  # Y has miss value already
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  data =  flashr2::flash_set_data(Y)
  g_flash = flashr2::flash_r1(data,verbose=F,var_type = "constant")
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}

@@

```{}
library(PMA)
library(flashr2)
library(ssvd)
source("../Rfunction.R")
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.7,c(1),c(1),1,sqrt(16))
# Data = datamaker(N,P,L_pi,L_se,0.1,c(1),c(1),1,sqrt(1))  sparse case
# Data = datamaker(N,P,L_pi,L_se,1.0,c(1),c(1),1,sqrt(1))  dense case
RMSE = rep(NA,6)
RMSE[1] = PMA.wrapper(Y_data)
RMSE[2] = flash.wrapper(Y_data)
RMSE[3] = SFA.wrapper(Y_data, K = 1)
RMSE[4] = SFAmix.wrapper(Y_data,K = 1)
RMSE[5] = SVD.wrapper(Y_data)
RMSE[6] = SSVD.wrapper(Y_data)
saveRDS(result, "./output.rds")
```

@@

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          axis.text.y = element_text(size =12),
          axis.text.x = element_text(size =12,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_sparse.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
methods_name = colnames(sparse_diff)
p1 = plot_res(sparse_diff,title = "Difference from FLASH result (90% zeros)",methods_name = methods_name)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p1_cut = plot_res(sparse_diff[-22,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (90% zeros)",methods_name = methods_name)
```

@@

methods_name = colnames(sparse_diff)
p2 = plot_res(sparse_diff,title = "Difference from FLASH result (30% zeros)",methods_name = methods_name)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p2_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (30% zeros)",methods_name = methods_name)
```

@@

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_dense.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
p3 = plot_res(sparse_diff,title = "Difference from FLASH result (0% zeros)",methods_name = methods_name)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p3_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (0% zeros)",methods_name = methods_name)
```

```{r}
# gridExtra::grid.arrange(p1,p2,p3,p1_cut,p2_cut,p3_cut,ncol = 3)
gridExtra::grid.arrange(p1,p1_cut,p2,p2_cut,p3,p3_cut,ncol = 2)
```

>>>>

---
title: "MSE for rank_1 simulation"
author: "wei wang"
output: 
  html_document:
    code_folding: hide
---

@@

PN.wrapper = function(Y_data){
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  library(ebnm)
  library(flashr)
  data =  flashr::flash_set_data(Y)
  g_flash = flashr::flash_r1(data,verbose=F,var_type = "constant",ebnm_fn = ebnm_pn)
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}

flash.wrapper = function(Y_data){
  # missindex is a matirx with 3 column here: i j x
  # Y has miss value already
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  data =  flashr::flash_set_data(Y)
  g_flash = flashr::flash_r1(data,verbose=F,var_type = "constant")
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}

@@

```{}
library(PMA)
library(flashr)
library(ssvd)
source("../Rfunction.R")
L_se = c( 0.25, 0.5, 1, 2, 4)
L_pi = c(1, 1,1,1,1)
L_pi = L_pi / sum(L_pi)
N = 200
P = 300
Data = datamaker(N,P,L_pi,L_se,0.7,c(1),c(1),1,sqrt(16))
# Data = datamaker(N,P,L_pi,L_se,0.1,c(1),c(1),1,sqrt(1))  sparse case
# Data = datamaker(N,P,L_pi,L_se,1.0,c(1),c(1),1,sqrt(25))  dense case
RMSE = rep(NA,6)
RMSE[1] = PMA.wrapper(Y_data)
RMSE[2] = flash.wrapper(Y_data)
RMSE[3] = SFA.wrapper(Y_data, K = 1)
RMSE[4] = SFAmix.wrapper(Y_data,K = 1)
RMSE[5] = SVD.wrapper(Y_data)
RMSE[6] = SSVD.wrapper(Y_data)
saveRDS(result, "./output.rds")
```

@@

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name,myColors){
  library(scales)
  modulus_trans <- function(lambda){
   trans_new("modulus",
             transform = function(y){
                if(lambda != 0){
                   yt <- sign(y) * abs(y)^(lambda)
                } else {
                   yt = sign(y) * (log(abs(y) + 1))
                }
                return(yt)
             },
             inverse = function(yt){
                if(lambda != 0){
                   y <- abs(yt)^(1/lambda) * sign(yt)
                } else {
                   y <- (exp(abs(yt)) - 1) * sign(yt)

                }
                return(y)
             }
             )
  }
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+ scale_color_manual(values=myColors)+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          axis.text.y = element_text(size =12.9),
          axis.text.x = element_text(size =15,angle = 45, hjust = 1),
          plot.title = element_text(size = 12.9, face = "bold")) + 
           scale_y_continuous(limits = c(-0.02,0.8), trans = modulus_trans(lambda = 0.5))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_sparse.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
methods_name = colnames(sparse_diff)
fill_color = c("red","yellow3", "springgreen", "springgreen3", "cyan","cyan3", "deepskyblue","violet","purple")
p1 = plot_res(sparse_diff,title = "Difference from flash result (90% zeros)",
              methods_name = methods_name, myColors = fill_color)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p1_cut = plot_res(sparse_diff[-22,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (90% zeros)",methods_name = methods_name,myColors = fill_color[c(1,2,3,4,5,7,9)])
```

@@

methods_name = colnames(sparse_diff)
p2 = plot_res(sparse_diff,title = "Difference from flash result (30% zeros)",methods_name = methods_name,myColors = fill_color)
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p2_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (30% zeros)",methods_name = methods_name,myColors = fill_color[c(1,2,3,4,5,7,9)])
```

@@

```{r}
sparse_res = readRDS("../data/simulation/rankone/RMSE/result_dense.rds")
colnames(sparse_res) = c("PMD.cv2","flash","SFA","flash.pn","SVD","SSVD","PMD.cv1","SFAmix","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
p3 = plot_res(sparse_diff,title = "Difference from flash result (0% zeros)",methods_name = methods_name,myColors = fill_color )
methods_name = colnames(sparse_diff)[c(1,2,3,4,5,7,9)]
p3_cut = plot_res(sparse_diff[,c(1,2,3,4,5,7,9)],title = "Difference from FLASH result (0% zeros)",methods_name = methods_name,myColors = fill_color[c(1,2,3,4,5,7,9)])
```

```{r}
# gridExtra::grid.arrange(p1,p2,p3,p1_cut,p2_cut,p3_cut,ncol = 3)
# gridExtra::grid.arrange(p1,p1_cut,p2,p2_cut,p3,p3_cut,ncol = 2)
gridExtra::grid.arrange(p1,p2,p3,ncol = 3)
```

### 2018-02-11 analysis/MSErank3sim.Rmd
Files commited by wflow_commit.

---
title: "MSE for rank_1 simulation"
author: "wei wang"
date: 18-01-23
output: 
  html_document:
    code_folding: hide
---

@@

PN.wrapper = function(Y_data,K = 3){
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  library(ebnm)
  library(flashr2)
  data =  flashr2::flash_set_data(Y)
  g_flash = flashr2::flash_add_greedy(data,verbose=F,var_type = "constant",ebnm_fn = ebnm_pn, K = K)
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}

flash.wrapper = function(Y_data, K = 3){
  # missindex is a matirx with 3 column here: i j x
  # Y has miss value already
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  data =  flashr2::flash_set_data(Y)
  g_flash = flashr2::flash_add_greedy(data,verbose=F,var_type = "constant", K = K)
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}
```

@@

```{}
library(PMA)
library(flashr2)
library(ssvd)
library(softImpute)
Y_data = DataMaker()
RMSE = rep(NA,6)
RMSE[1] = PMA.wrapper(Y_data)
RMSE[2] = flash.wrapper(Y_data)
RMSE[3] = PN.wrapper(Y_data)
RMSE[4] = SVD.wrapper(Y_data)
RMSE[5] = SSVD.wrapper(Y_data)
RMSE[6] = softImpute.wrapper(Y_data)
saveRDS(RMSE, "./output.rds")
```

@@

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          plot.title = element_text(size = 18, face = "bold"),
          axis.text.y = element_text(size =15), 
          axis.text.x = element_text(size =15,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/simulation/rankthree/boxplot.rds")
colnames(sparse_res) = c("PMD.cv1","flash","flash.pn","SVD","SSVD","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
p3 = plot_res(sparse_diff,title = "Rank 3 example",methods_name = methods_name)
```

```{r}
p3
```

>>>>

---
title: "MSE for rank_1 simulation"
author: "wei wang"
output: 
  html_document:
    code_folding: hide
---

@@

PN.wrapper = function(Y_data,K = 3){
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  library(ebnm)
  library(flashr)
  data =  flashr::flash_set_data(Y)
  g_flash = flashr::flash_add_greedy(data,verbose=F,var_type = "constant",ebnm_fn = ebnm_pn, K = K)
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}

flash.wrapper = function(Y_data, K = 3){
  # missindex is a matirx with 3 column here: i j x
  # Y has miss value already
  Y = Y_data$Y
  L_true = Y_data$L_true
  F_true = Y_data$F_true
  E = Y_data$E
  N = dim(Y)[1]
  P = dim(Y)[2]
  data =  flashr::flash_set_data(Y)
  g_flash = flashr::flash_add_greedy(data,verbose=F,var_type = "constant", K = K)
  Y_hat = g_flash$EL %*% t(g_flash$EF)
  RMSE = sqrt(mean(( Y - Y_hat - E )^2 ))/sqrt(mean(( Y - E )^2 ))
  return(RMSE)
}
```

@@

```{}
library(PMA)
library(flashr)
library(ssvd)
library(softImpute)
Y_data = DataMaker()
RMSE = rep(NA,6)
RMSE[1] = PMA.wrapper(Y_data)
RMSE[2] = flash.wrapper(Y_data)
RMSE[3] = PN.wrapper(Y_data)
RMSE[4] = SVD.wrapper(Y_data)
RMSE[5] = SSVD.wrapper(Y_data)
RMSE[6] = softImpute.wrapper(Y_data)
saveRDS(RMSE, "./output.rds")
```

@@

```{r}
plot_res = function(output,title = "data",legend_position = "none", methods_name,myColors){
  rmse = as.vector(output)
  N = dim(output)[1]
  methods = rep(methods_name, each = N)
  df = data.frame(RRMSE_diff = rmse, Method = methods )
  p<-ggplot(df, aes(x=Method, y=RRMSE_diff, color=Method)) +
  geom_boxplot()+
  # geom_violin()+
  ggtitle(title) +  theme_bw()+ scale_color_manual(values=myColors)+
    theme(legend.position= legend_position, legend.text=element_text(size=10),
          plot.title = element_text(size = 12.9, face = "bold"),
          axis.text.y = element_text(size =12), 
          axis.text.x = element_text(size =12,angle = 45, hjust = 1))
  p
}
library(ggplot2)
```

```{r}
sparse_res = readRDS("../data/output/simulation/rankthree/boxplot.rds")
colnames(sparse_res) = c("PMD.cv1","flash","flash.pn","SVD","SSVD","SI.cv")
sparse_diff = sparse_res - sparse_res[,2]
# p3 = plot_res(sparse_diff,"Difference from FLASH result (0% zeros)")
methods_name = colnames(sparse_diff)
fill_color =  c("red","yellow3", "springgreen", "springgreen3", "cyan","cyan3", "deepskyblue","violet","purple")
p3mse = plot_res(sparse_diff,title = "Box plot of RRMSE compared with flash",methods_name = methods_name,
              myColors = fill_color[c(1,2,3,7,8,9)])
```

```{r}
p3mse
```

### 2018-02-11 analysis/index.Rmd
Files commited by wflow_commit.

@@

### Apply flashr2 for the examples in FLASH paper

@@

Click here to check the [simulatoin result (rank one and rank three)](applyflahr2onsimulations.html)

@@

Here is a example to run `flashr2` on RCC [RCC template](GTEXzscoreTemplate.html)

@@

click here to check the comparison of different options for FLASH [different shrink options](compareOptionsOCV.html)

>>>>

[old experiments](oldanalysis.html)

@@

### Apply flashr for the examples in FLASH paper

@@

@@

Here is a example to run `flashr` on RCC [RCC template](GTEXzscoreTemplate.html)

@@

### 2018-02-11 analysis/setup.Rmd
Files commited by wflow_commit.

*Fill out setup instructions in this section. See
[here](https://stephenslab.github.io/wflow-divvy/setup.html) and
[here](https://github.com/pcarbo/mouthwash_sims/blob/master/README.md)
for some ideas.*

@@

>>>>

### Install software and R packages

1. Install [R](https://cran.r-project.org).

2. Install [MATLAB](https://www.mathworks.com/products/matlab.html)

3. Install the required R packages (run the following commands in the R).

```R
install.packages(c("devtools", "ashr", "PMA","ssvd","softImpute","Matrix","R.matlab","ggplot2","denoiseR"))
devtools::install_github("stephenslab/flashr")
```

4. Install MATLAB package [NBSFA](https://github.com/davidaknowles/nsfa)

5. Install packages [sfa](http://stephenslab.uchicago.edu/software.html#sfa) and [SFAmix](http://beehive.cs.princeton.edu/software/)

### Data sets

All the data sets used in the paper are in [data files](https://github.com/NKweiwang/flash_workflow/tree/master/data/output/missingdata)

@@

```{r,echo=FALSE}
library(flashr)
library(ssvd)
library(methods)
library(PMA)
library(R.matlab)
library(Matrix)
library(softImpute)
library(ggplot2)
library(denoiseR)
```
